Human Capital Model

### 2015-02-09 paper.tex
add analysis 3~5

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

@@

\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

>>>>

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{booktabs}
\usepackage{caption2}
\usepackage{epstopdf}
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\renewcommand{\captionlabelfont}{\small \bfseries \rmfamily}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company. With these two assumption, results can be drawn according to our model through simulation.

Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.

\begin{tabular}{*{4}{c}}\toprule[2pt]
Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
\end{tabular}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_p.pdf}\\
  \caption{Status of positions}\label{t4_p}
\end{figure}

To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints. We execute our program 100 times for each churn rate and average the predicted values. Figure \ref{t4_p} shows the averaged results our model predicted. Under all of these three conditions, the number of employees in the company keeps rising. The higher the churn rate, the lower the final full rate the company reaches after two years. But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_r.pdf}\\
  \caption{Recruiting budget}\label{t4_r}
\end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=7cm]{task4_t.pdf}
  \includegraphics[width=7cm]{task4_s.pdf}\\
  \caption{Training budget and salary budget}\label{t4_t_s}
\end{figure}
The churn rate effect the budget of the company as well. The three parts of the bugdet behave differently when churn rate increases. The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}. Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart. It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.

To maintain enough employees, the company has to spend more on recruiting. So high turnover rate directly increase the recruiting budget. High turnover rate's effect on training budget and salary budget is more complex. On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate. On the other hand, the vacancies in lower level remains low because of the short recruiting time. So the full rate of the company decreases when churn rate rises. Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task5_p.pdf}\\
  \caption{Status of position}\label{t5_p}
\end{figure}
We apply following changes to our model to simulate the required process:\\
\begin{itemize}
\item Change the churn rate of junior managers and experienced supervisors to 30\%
\item Prohit external recruiting
\item Promoting only qualified employees
\end{itemize}
\begin{table}
	\begin{center}
		\begin{tabular}{l|cc}\toprule[2pt]
		\bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
		Senior manager/Executive & 5.6 & 8.4\\
		Junior manager/Executive & 9.0 & 18.4\\
		Experienced supervisor & 7.4 & 23.0\\
		Inexperienced supervisor & 9.2 & 23.2\\
		Experienced employee & 72.6 & 107.4\\
		Inexperienced employee & 99.6 & 149.6\\
		Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
		\end{tabular}
		\caption{Status of position}\label{t5_p_t}
	\end{center}
\end{table}

The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}. All the data shown is an average of ten predictions. While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.

We list specific data of each level in Table \ref{t5_p_t}. In the modified case, the numbers of employees are lower than original case especially the those of middle levels. Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave. Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low. The situation given in that task 5 will cause unrecoverable damage to ICM's HR health. With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.
